### 2013-02-16 doc/icml2013/evaluation.tex
edit

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent
algorithm.%\cite{candes11phaselift,tomioka2010estimation}. (Note sure about this citation and not required?)
The algorithm
was initialized with the regularized least squares solution and was run
for 500 steps or till convergence. Both regularization parameters,
$\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as $\frac{1}{n}$.

@@

We generated synthetic data using covariates from the $b$-dimensional
unit hyper cube $\{-1,1\}^b$ and considered non-linear featurizations of
this data that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}. The $\beta$ were drawn from a standard Gaussian.

@@

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between SpectralExperts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\begin{figure*}[tb]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovey error vs $n$  ($b = 1, d = 5, K = 3, N = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

In \figureref{fig:vs-n}, we show how the recovery error varies as we get
more data. Each data point shows the mean error over 10 attempts, with
error bars. We note that the recovery performance of EM does not
particularly improve; this is expected because of the problem of local
optima. The spectral algorithm's error decays slowly, and as it gets
closer to zero, EM initialized at the spectral parameters finds the true
parameters more often as well. This behaviour highlights the trade-off
between statistical and computational error.

>>>>

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent
algorithm.%\cite{candes11phaselift,tomioka2010estimation}. (Note sure about this citation and not required?)
The algorithm
was initialized with the regularized least squares solution and was run
for 500 iterations or until convergence up to a tolerance of $10^{-3}$. Both regularization parameters,
$\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as $\frac{1}{n}$.

@@

We generated synthetic data using covariates $x$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$ and considered non-linear featurizations of
this data that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}. The coefficients $\{\beta_h\}$ were drawn from a standard Gaussian.

@@

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between Spectral Experts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\begin{figure*}[tb]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovery error vs $n$  ($b = 1, d = 5, K = 3, N = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

In \figureref{fig:vs-n}, we show how the recovery error varies as we get
more data. Each data point shows the mean error over 10 attempts, with
error bars. We note that the recovery performance of EM does not
particularly improve; this is expected because of the problem of local
optima. The spectral algorithm's error decays slowly, and as it gets
closer to zero, EM initialized at the spectral parameters finds the true
parameters more often as well. This behavior highlights the trade-off
between statistical and computational error.
